\begin{resumo}[Abstract]
 \begin{otherlanguage*}{english}
This study aimed to develop a multiparadigm software to operate automated form the Currency Market: InvestMVC software. A research methodology based on objective and based on the technical procedures was adopted. Based on the goals it was incorporated an exploratory and descriptive research. Regarding the technical procedures we used a case study, because although this work have had a quantitative data approach and involvement of Mathematical Methods for preparation of financial strategies, you can not say that the results can be generalized to other contexts, for example to other market than the Currency Market on the pair of euro-dollar trading. To conduct the research, an adaptation of Scrum was carried out, taking into account the activities allocated on schedule with the development of User Stories and tasks. Through the case study protocol was defined methodological steps to meet specific goals and answer the research question of this work. Methods software operating Mathematical InvestMVC and the comparison of monetary results with expert MQL were the most significant results that helped to answer the research question. Other results as architecture, unit testing and static analysis of source code, also added a lot of value to work. It was also evidenced attributes InvestMVC software, such as creating an account, log in, create an expert, the expert view and enable it to perform automated operations. Finally, the conclusion was reported.
   \vspace{\onelineskip}
 
   \noindent
   \textbf{Key-words}: FOREX, Mathematical Methods, Programming Paradigms, Software Quality.
 \end{otherlanguage*}
\end{resumo}
